Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-03 sections/related.tex
cool

\paragraph{Other Architectures:} We would be remiss if we didn't mention another axis: architectural support. 
%
We saved this angle for future work, but we must note that much of this work varies in support for other architectures, which is arguably another element of control flow.
%%TACO
%%Tiachi
%%SPF
%%Stut
%%Graphit
%%Spiral
%%SQL

>>>>

\paragraph{Other Architectures:}

Both structured and dense libraries support a multitude of architectures, as do dense compilers.

Sparse compilers have been extended to many architectures. An extension of TACO supports GPU \cite{senanayake2020sparse}, Cyclops\cite{solomonik_cyclops_2013,solomonik_sparse_2015} and SPDistal\cite{yadav_spdistal_2022-1} support distributed memory, and the Sparse Abstract Machine\cite{hsu_sparse_2022} supports custom hardware.

We believe that supporting control flow is the first step towards architectural support for complex structures.

%Sparse and structured com We would be remiss if we didn't mention another axis: architectural support. 
%
%We saved this angle for future work, but we must note that much of this work varies in support for other architectures, which is arguably another element of control flow.
%%TACO
%%Tiachi
%%SPF
%%Stut
%%Graphit
%%Spiral
%%SQL
